\begin{problem}
 {\bf Semi-infinite square-well potential.} Download the Excel worksheet
\verb+semi-finite.xls+ from either the {\it Handouts} page or from the
Calendar page.  This sheet shows the calculations for determining the
wavefunctions for a potential well that is infinite at $x=0$ but of 
finite magnitude on the right side of the well (which is at $x=5$ in
this problem).  You'll see two
graphs: the top one shows the semi-infinite potential well (in
purple) along with a non-normalized plot of the calculated
wavefunction so you can see it along with the potential.  The bottom
graph shows the normalized wavefunction, corresponding to the
second-to-last column in the worksheet.  

When you bring up the worksheet, the energy will be set for the
value for the ground state.  Some questions:

\begin{enumerate}

\item Sketch or print out (just the first page!) the wavefunctions 
that are displayed for the ground state along with at least two 
of the excited states.  To display
the 1$^{\rm st}$ and $2^{\rm nd}$ excited states, type in 0.64282 and 
1.4144 respectively in the framed box for energy.  

\item What happens if you type in an energy that {\bf isn't} one
of the well-defined energies for the problem?  Try it out, and
comment on what happens.  Had we not told you what the allowed
energies were, how might you figure them out?  (You'll be doing
this in lab later this semester.)

\item For any of the allowed states, show that the state plotted
in the bottom graph is normalized.  Hint:  we have already created a
column for the square of the normalized wavefunction (the
right-most column).  You might want to take advantage of the
\verb+sum(start:end)+ routine in Excel.

\end{enumerate}
